Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-08 paper/paper.tex
updated table V

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & JerryScript      \\
   2  & 4/23 & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & 2 & Mozilla      \\
   3  & 4/29 & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & 2 & Mozilla \\
   \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & \multirow{2}{*}{2} & \multirow{2}{*}{Mozilla}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &   & \\
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & Mozilla \\
   6 & 5/17  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & 2 & Mozilla\\
   8 & 6/28  & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & 2 & JerryScript\\
   10 & 7/18  & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & 2 & Mozilla\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & JerryScript\\
   12 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & - & JerryScript\\
   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & JerryScript\\
   14 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & - & JerryScript\\
   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & JerryScript\\
   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & JerryScript\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
    & \Fix{x} & LO & WebKit \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
    & \Fix{x} & HI & WebKit \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & \Fix{x}  & HI & WebKit    \\
    4  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
    & \Fix{x} & HI & JerryScript   \\
    5  & 4/29 & radamsa & JavascriptCore  & New  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & \Fix{x}  & HI  & JerryScript\\
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
    & \Fix{x} & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & \Fix{x} &  & \\
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & \Fix{x} & LO & Mozilla \\
    8 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
    & \Fix{x} & HI & JerryScript \\
    9 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
    & \Fix{x} & HI & V8\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & \Fix{x} & HI & Webkit\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & \Fix{x} & HI & JerryScript\\
    12 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & \Fix{x} & HI & JerryScript\\
    13 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
    & \Fix{x} & HI & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

>>>>

\begin{table*}[t]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of test transplantation.}
  \label{tab:test-transplantation-bugs}
  \begin{tabular}{cccccccc}
    \toprule Issue\#    & Date & Engine  & Status  & \multicolumn{1}{c}{Url}  & Severity & Suite \\
    \midrule    
    1  & 4/18  & JavascriptCore  & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}} & - & JerryScript      \\
   2  & 4/23 & Chakra  & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}} & 2 & \smonkey{}      \\
   3  & 4/29 & Chakra  & \textbf{Confirmed}   &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}} & 2 & \smonkey{} \\
   \midrule
    \multirow{2}{*}{4}  & \multirow{2}{*}{4/29} & Chakra & \textbf{Confirmed} &    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067}} & 2 & \multirow{2}{*}{\smonkey{}}\\
                       &  &
    JavascriptCore & New &    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130} } &  -  & \\
   \midrule
   5 & 5/02  & JavascriptCore & New  & \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}} & - & \smonkey{} \\
   6 & 5/17  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187}} & 2 & \jsc{}\\
   7 & 5/21  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203}} & 2 & \smonkey{}\\
   8 & 6/28  & Chakra & \textbf{Confirmed}  & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388}} & 2 & \jsc{}\\
   9 & 7/10  & Chakra & \textbf{Confirmed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5442}{\#5442}} & 2 & JerryScript\\
   10 & 7/18  & Chakra & \textbf{Fixed} & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5478}{\#5478}} & 2 & \smonkey{}\\
   11 & 7/18  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187777}{\#187777}} & - & JerryScript\\
   12 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5576}{\#5576}} & - & JerryScript\\
   13 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188378}{\#188378}} & - & JerryScript\\
   14 & 8/07  & Chakra & New & \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5579}{\#5579}} & - & JerryScript\\
   15 & 8/07  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188382}{\#188382}} & - & JerryScript\\
   16 & 8/08  & V8 & \textbf{Confirmed} & \anonym{\href{https://bugs.chromium.org/p/v8/issues/detail?id=8033}{\#8033}} & 3 & JerryScript\\
   17 & 8/08  & JavascriptCore & New & \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=188407}{\#188407}} & - & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued as result of cross-engine
    differential testing.}
  \label{tab:bugs}
  \begin{tabular}{ccccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  &
    \multicolumn{1}{c}{Url}  & Severity & Priority & Suite \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}}
    & 2 & LO & \jsc{} \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}}
    & - & HI & \jsc{} \\
    3  & 4/14 & radamsa & JavascriptCore  & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}
    } & -  & HI & \jsc{}    \\
    4  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}}
    & 2 & HI & JerryScript   \\
    5  & 4/29 & radamsa & JavascriptCore  & New  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}
    } & -  & HI  & JerryScript\\
    \midrule
    \multirow{2}{*}{6} & \multirow{2}{*}{4/30}  &
    \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076}}
    & 2 & \multirow{2}{*}{HI} & \multirow{2}{*}{TinyJS}\\    
                        &                        &        &
    JavascriptCore & New &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}}
    & - &  & \\
    \midrule
    7 & 5/02 & radamsa & JavascriptCore  & \textbf{Fixed} &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}}
    & 2 & LO & \smonkey{} \\
    8 & 5/10 & radamsa & Chakra & \textbf{Confirmed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128}}
    & 3 & HI & JerryScript \\
    9 & 5/17 & radamsa & Chakra & \textbf{Fixed} &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182}}
    & 2 & HI & \veight{}\\
    10 & 5/24 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}}
    & 2 & HI & \jsc{}\\
    11 & 6/26 & radamsa & JavascriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042}}
    & 2 & HI & JerryScript\\
    12 & 7/10 & quickfuzz & JavaScriptCore & \textbf{Fixed}  &
    \anonym{\href{https://bugs.webkit.org/show_bug.cgi?id=187520}{\#187520}}
    & 2 & HI & JerryScript\\
    13 & 7/10 & quickfuzz & Chakra & \textbf{Confirmed}  &
    \anonym{\href{https://github.com/Microsoft/ChakraCore/issues/5443}{\#5443}}
    & 2 & HI & JerryScript\\
   \bottomrule
  \end{tabular}
\end{table*}
